BOAST: a Metaprogramming Framework to Produce Portable and Efficient Computing Kernels for HPC Applications

### 2014-07-07 Paper/BOAST.tex
update to paper

Developed by physicist, chemist, meteorologist. Usually in FORTRAN for
historical and performance reason. Codes can be quite huge (several
thousands lines of code) with lots of functionalities. Nonetheless they are
usually based on computing kernels. Computing kernels are resource
intensive well defined parts of a program.

  \subsection{One extreme case: the Mont-Blanc prototype}

>>>>

Developed by physicist, chemist, meteorologist. Usually in FORTRAN for
historical and performance reason. Codes can be quite huge (several
thousands lines of code) with lots of functionalities. Nonetheless they are
usually based on computing kernels. Computing kernels are resource
intensive well defined parts of a program with a limited set of input and
output. Those kernels are the time consuming part of an HPC application.

  \subsection{Performance Portability of Computing Kernels}
